---
title: "PCA"
author: "Ted"
date: "2018年7月23日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## General methods for principal component analysis

### prcomp() and princomp() functions

```{r, eval = FALSE}
prcomp(x, scale = FALSE)
princomp(x, cor = FALSE, scores = TRUE)

```

Arguments for prcomp():
x: a numeric matrix or data frame
scale: a logical value indicating whether the variables should be scaled to have unit variance before the analysis takes place

Arguments for princomp():
x: a numeric matrix or data frame
cor: a logical value. If TRUE, the data will be centered and scaled before the analysis
scores: a logical value. If TRUE, the coordinates on each principal component are calculated

prcomp() name | princomp() name |	Description
--- | --- | ---
sdev | sdev	| the standard deviations of the principal components
rotation | loadings |	the matrix of variable loadings (columns are eigenvectors)
center | center	| the variable means (means that were substracted)
scale	| scale	| the variable standard deviations (the scaling applied to each variable )
x	| scores	| The coordinates of the individuals (observations) on the principal components.

### PCA visualization

use the factoextra R package to create a ggplot2-based elegant visualization.

1. Load the data
2. Load factoextra for visualization
3. Compute PCA
4. Visualize eigenvalues (scree plot). Show the percentage of variances explained by each principal component.
5. Graph of individuals. Individuals with a similar profile are grouped together.
6. Graph of variables. Positive correlated variables point to the same side of the plot. Negative correlated variables point to opposite sides of the graph.
7. Biplot of individuals and variables

```{r, message=FALSE, error=FALSE, warning=FALSE, eval=FALSE}
install.packages("factoextra")
# OR
if(!require(devtools)) install.packages("devtools")
devtools::install_github("kassambara/factoextra")
# then
library(factoextra)
```

```{r, message=FALSE, error=FALSE, warning=FALSE,}
library("factoextra")
data(decathlon2)
decathlon2.active <- decathlon2[1:23, 1:10]
head(decathlon2.active[, 1:6])
```

```{r, message=FALSE, error=FALSE, warning=FALSE,echo=FALSE }
library(factoextra)
```

```{r, message=FALSE, error=FALSE, warning=FALSE,}
res.pca <- prcomp(decathlon2.active, scale = TRUE)  # Compute PCA

fviz_eig(res.pca)  # Visualize eigenvalues

fviz_pca_ind(res.pca,
             col.ind = "cos2", # Color by the quality of representation
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE     # Avoid text overlapping
             )  # Graph of individuals

fviz_pca_var(res.pca,
             col.var = "contrib", # Color by contributions to the PC
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE     # Avoid text overlapping
             )  # Graph of variables

fviz_pca_biplot(res.pca, repel = TRUE,
                col.var = "#2E9FDF", # Variables color
                col.ind = "#696969"  # Individuals color
                )  # Biplot of individuals and variables
```

### Access to the PCA results

```{r}
library(factoextra)

# Eigenvalues
eig.val <- get_eigenvalue(res.pca)
head(eig.val)
  
# Results for Variables
res.var <- get_pca_var(res.pca)
head(res.var$coord)          # Coordinates
head(res.var$contrib)        # Contributions to the PCs
head(res.var$cos2)           # Quality of representation 
# Results for individuals
res.ind <- get_pca_ind(res.pca)
head(res.ind$coord)          # Coordinates
head(res.ind$contrib)        # Contributions to the PCs
head(res.ind$cos2)           # Quality of representation 

```

### Predict using PCA

We’ll show how to predict the coordinates of supplementary individuals and variables by the previously performed PCA.

### Theory behind PCA results

#### PCA results for variables

here we’ll show how to calculate the PCA results for variables: coordinates, cos2 and contributions:

1. `var.coord` = loadings * the component standard deviations
2. `var.cos2` = var.coord^2
3. `var.contrib`  The contribution of a variable to a given principal component is (in percentage) : (var.cos2 * 100) / (total cos2 of the component)

#### PCA results for individuals

1. `ind.coord` = res.pca$x
2. Cos2 of individuals. Two steps:
  
  * Calculate the square distance between each individual and the PCA center of gravity: d2 = [(var1_ind_i - mean_var1)/sd_var1]^2 + …+ [(var10_ind_i - mean_var10)/sd_var10]^2 + …+..
  * Calculate the cos2 as ind.coord^2/d2
3. Contributions of individuals to the principal components: 100(1 / number_of_individuals)(ind.coord^2 / comp_sdev^2) 

*Note that the sum of all the contributions per column is 100*