---
title: "Reporting With Rmarkdown 學習筆記"
author: "Ted"
date: "July 15, 2018"
output: html_document
---
## RMarkdown
********

RMarkdown是一種編寫格式，他比HTML容易閱讀編寫，但不是來取代HTML的。編寫完的RMarkdown可以以word, HTML, pdf 等形式發布


## Basic Format
****

* A YAML header that contains some metadata
* Narrative text written in Markdown
* R code chunks surrounded by ```{r} and ```; a syntax that comes from the knitr package


## 自製cheatsheet
*****

### **標題**
*******

```{r}
# First level header
## Second level header
### Third level header
```
# First level header
## Second level header
### Third level header

### **字體**
********

```{r}
# 斜體*italics*
# 粗體**bold**
# monospaced(像編碼):`code`
```
*italics*
**bold**
`code`

### **超連結**
*****

```{r}
# [RStudio](www.rstudio.com)
# 中括號內放名稱；小括號放link
```
[RStudio](www.rstudio.com)

### **清單**
********

```{r}
# 1. item 1
# 2. item 2
# 3. item 3
# * item 1
# * item 2
# * item 3
```

**打清單前要記得空一行you need to place a blank line between the list and any paragraphs that come before it**

1. item 1
2. item 2
3. item 3
* item 1
* item 2
* item 3

### **加入數學式LaTeX equations**
******

```{r}
# $$1+1 = 2$$
# 插入兩個$在兩端
# LaTeX 可以拿來打方程式，很好用
```
[LaTeX/Mathematics](https://en.wikibooks.org/wiki/LaTeX/Mathematics)

### **knitr syntax**knitr語法
*****

```{r}
# 加入code
# code chunk:```{r, chunk option }code```
# embed in text:`r 文字`
```
chunk option:

* 輸出結果:

  1. message = FALSE
  2. error = FALSE
  3. warning = FALSE
  4. echo = FALSE**不顯示code, 只呈現結果**
  5. eval = FALSE**不跑, 但會顯示code**
  6. result = "hide"**跑code，但不顯示結果**
