---
title: "TFIDFguide"
author: "Ted"
date: "2018年7月23日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###  Analyzing word and document frequency: tf-idf
The statistic tf-idf is intended to measure how important a word is to a document in a collection (or corpus) of documents

1. term frequency (tf), how frequently a word occurs in a document
2. inverse document frequency (idf):
decreases the weight for commonly used words and increases the weight for words that are not used very much in a collection of documents.
<p><span class="math display">\[idf(\text{term}) = \ln{\left(\frac{n_{\text{documents}}}{n_{\text{documents containing term}}}\right)}\]</span></p>

### Term frequency in Jane Austen’s novels

```{r,message=FALSE,warning=FALSE,error=FALSE}
library(dplyr)
library(janeaustenr)
library(tidytext)

book_words <- austen_books() %>%
  unnest_tokens(word, text) %>%
  count(book, word, sort = TRUE) %>%
  ungroup()

total_words <- book_words %>% 
  group_by(book) %>% 
  summarize(total = sum(n))

book_words <- left_join(book_words, total_words)
```
```{r}
book_words
```
`n `:the number of times that word is used in that book
`total`: the total words in that book

term frequency: look at the distribution of n/total for each novel
```{r,message=FALSE, warning=FALSE}
library(ggplot2)

ggplot(book_words, aes(n/total, fill = book)) +
  geom_histogram(show.legend = FALSE) +
  xlim(NA, 0.0009) +
  facet_wrap(~book, ncol = 2, scales = "free_y")
```

**Zipf’s law**  states that the frequency that a word appears is inversely proportional to its rank.

<mtext>frequency</mtext>
  <mo>&#x221D;<!-- ∝ --></mo>
  <mfrac>
    <mn>1</mn>
    <mtext>rank</mtext>
  </mfrac>
</math>
```{r,warning=FALSE}
freq_by_rank <- book_words %>% 
  group_by(book) %>% 
  mutate(rank = row_number(), 
         `term frequency` = n/total)

head(freq_by_rank)
```
The `rank `column here tells us the rank of each word within the frequency table

### The bind_tf_idf function

bind_tf_idf function (tidytext package) takes a tidy text dataset as input with
1. one row per token (term), per document. 
2. One column (`word` here) contains the terms/tokens, 
3. one column contains the documents (`book` in this case), 4. column contains the counts, how many times each document contains each term (`n`in this example).

```{r, message=FALSE, warning=FALSE}
book_words <- book_words %>%
  bind_tf_idf(word, book, n)
book_words
```

```{r, warning=FALSE}
# high tf-idf in Jane Austen’s works
book_words %>%
  select(-total) %>%
  arrange(desc(tf_idf))
```
visualization for these high tf-idf words
```{r,message=FALSE,warning=FALSE}
book_words %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>% 
  group_by(book) %>% 
  top_n(15) %>% 
  ungroup %>%
  ggplot(aes(word, tf_idf, fill = book)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~book, ncol = 2, scales = "free") +
  coord_flip()
```

### A corpus of physics texts

1. load text
2. Use `unnest_tokens()` and `count()` to find out how many times each word was used in each text.
3. Clean up the text
4. Calculate tf-idf, then visualize the high tf-idf words

```{r,message=FALSE,warning=FALSE,error=FALSE}
library(gutenbergr)
physics <- gutenberg_download(c(37729, 14725, 13476, 5001), meta_fields = "author")
```
```{r,warning=FALSE}
physics_words <- physics %>%
  unnest_tokens(word, text) %>%
  count(author, word, sort = TRUE) %>%
  ungroup()

head(physics_words)
```

```{r, warning=FALSE}
# Notice that we make a custom list of stop words and use anti_join() to remove them
library(stringr)

mystopwords <- data_frame(word = c("eq", "co", "rc","ac", "ak", "bn", "fig", "file", "cg", "cb", "cm"))
physics_words <- anti_join(physics_words, mystopwords, by = "word")
```

```{r, message=FALSE, warning=FALSE}
plot_physics <- physics_words %>%
  bind_tf_idf(word, author, n) %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>%
  group_by(author) %>% 
  top_n(15, tf_idf) %>%
  ungroup %>%
  mutate(author = factor(author, levels = c("Galilei, Galileo","Huygens, Christiaan","Tesla, Nikola","Einstein, Albert")))

ggplot(plot_physics, aes(word, tf_idf, fill = author)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~author, ncol = 2, scales = "free") +
  coord_flip()
```